|

### 2019-12-28 article/article.Rmd
small edits to article and letter

The first intervention was carried out from August 2017 to July 2018 using the
Android version of TDP. The randomization was conduct at the municipal level.
We randomly selected `r as.numeric(table(impact_evaluation_phase1$treat)[1])`
municipalities to the control group and included 
`r format(as.numeric(table(impact_evaluation_phase1$treat)[2]),
big.mark = ",")` in the treatment group. Our control condition consists in
removing all information about school construction from the TDP app in the
chosen municipalities, so that citizens were unable to report constructions in
the control municipalities.

To evaluate the random assignment, we used the following pre-treatment
variables: 1) log of municipal population in 2015; 2) log of number of poor
families in each city; 3) log of total federal transfers to the municipality in
2016; 4) federal government indicator for primary school quality; 5) federal
government indicator for secondary school quality. The data come from the
Brazilian Ministry of Education and the Census. Balance tests show that the
randomisation was successful and are available in the Supplementary Materials.

@@

**Data from Google Analytics suggest that users did engage with the TDP app. On
average, each user launched `r format(round(mean(as.numeric(gsub('\\.', '',
ga2$visualizacoes_de_tela))), 2), big.mark = ",")` app sessions, which
indicates their interest in the application. In total, the app had 
`r format(sum(as.numeric(gsub('\\.', '', ga2$visualizacoes_de_tela))),
big.mark = ",", scientific = F)` screen visualisations, with an average of 
`r round(mean(as.numeric(gsub(',', '.', ga2$telas_sessao))), 2)` screen
visualisations per session.**

@@

What factors, then, are driving these results? It seems unlikely that the null
results derive from flaws in the research design. First, our study is well
powered. Although the treatment is indirect---the person has to download the
app, find a school construction, and then report it---,we included
a substantial number of schools in the treatment groups. Second, balance and
manipulation tests indicate that the treatment allocation was successful, so we
can rule out problems in the randomisation procedures. **Third, data from
Google Analytics confirm that citizens did use the app and provided information
to our dataset. This indicates that the treatment manipulation was effective.
In this sense, it is unlikely that our results derive from low user response.**
Fourth, after doing a series of robustness tests, we still find no firm
evidence of treatment effect. Finally, note that the sign of the coefficients
are frequently contrary to our theoretical expectations. This rules out
a possible concern about statistical power with our small control group
approach.

>>>>

The first intervention was carried out from August 2017 to July 2018 using the
Android version of TDP. The randomisation was conducted at the municipal level.
We randomly selected `r as.numeric(table(impact_evaluation_phase1$treat)[1])`
municipalities to the control group and included 
`r format(as.numeric(table(impact_evaluation_phase1$treat)[2]),
big.mark = ",")` in the treatment group. Our control condition consists in
removing all information about school construction from the TDP app in the
chosen municipalities, so that citizens were unable to report constructions in
the control municipalities.

To evaluate the random assignment, we used the following pre-treatment
variables: 1) log of municipal population in 2015; 2) log of number of poor
families in each city; 3) log of total federal transfers to the municipality in
2016; 4) federal government indicator for primary school quality; 5) federal
government indicator for secondary school quality. The data come from the
Brazilian Ministry of Education and the 2010 Brazilian Census. Balance tests
show that the randomisation was successful and are available in the
Supplementary Materials.

@@

**Data from Google Analytics suggest that users did engage with the TDP app. On
average, each user launched `r format(round(mean(as.numeric(gsub('\\.', '',
ga2$visualizacoes_de_tela))), 1), big.mark = ",")` app sessions, which
indicates their interest in the application. In total, the app had 
`r format(sum(as.numeric(gsub('\\.', '', ga2$visualizacoes_de_tela))),
big.mark = ",", scientific = F)` screen visualisations, with an average of 
`r round(mean(as.numeric(gsub(',', '.', ga2$telas_sessao))), 2)` screen
visualisations per session.**

@@

What factors, then, are driving these results? It seems unlikely that the null
results derive from flaws in the research design. First, our study is well
powered. Although the treatment is indirect---the person has to download the
app, find a school construction, and then report it---,we included
a substantial number of schools in the treatment groups. Second, balance and
manipulation tests indicate that the treatment allocation was successful, so we
can rule out problems in the randomisation procedures. **Third, data from
Google Analytics confirm that citizens indeed used the app and provided
information to our dataset. This indicates that the treatment manipulation was
effective. In this sense, it is unlikely that our results derive from low user
response.** Fourth, after doing a series of robustness tests, we still find no
firm evidence of treatment effect. Finally, note that the sign of the
coefficients are frequently contrary to our theoretical expectations. This
rules out a possible concern about statistical power with our small control
group approach.

### 2019-12-28 article/letter.Rmd
small edits to article and letter

\noindent 25 December 2019

@@

Lastly, we have rewritten some parts of the main text to highlight two points:
1) that our experiment hinges on participation only; 2) that the effect of
mobilisation and pressure on school construction outcomes require further
analyses. We believe our paper now reflects our results more accurately.

Below we discuss in more detail these and other changes we have made to the
manuscript in response to comments from the editor and the reviewer. We thank
the editor again for the opportunity to revise the manuscript, and the reviewer
for his/her extremely helpful comments.

@@

> We have made several changes to the main paper and the online appendix to
address this important concern. First, we have added a new section to the
appendix (B) in order to clarify how we designed and conducted the experiment.
We copy the text below:

@@

> To answer these questions, we have added Google Analytics data on _Tá de
Pé_'s download and usage. This provide reliable and exogenous data
about our experimental manipulation and the effectiveness of the treatment. The
data confirm that app usage was significant. We add the following paragraph to
the main text to show user engagement (page 8):

@@

> _Data from Google Analytics suggest that users did engage with the TDP app.
On average, each user launched 59.99 app sessions, which indicates their
interest in the application. In total, the app had 53,928 screen
visualisations, with an average of 2.42 screen visualisations per session._

@@

> We fully agree with the reviewer and have changed the main text accordingly.
We have rewritten several passages, from the abstract to the discussion, in
order to highlight that our mechanism is indeed based on information provision
and not exactly mobilisation. For instance, the first paragraph in the
Discussion session has been rewritten as:

@@

@@

Our explanation of the results on page 9 has been rewritten as:

@@

> The reviewer finally questions us about the possibility of cross-municipality
> contamination. This would mean that the existence of the app in a
> municipality could make mayors in other municipalities to act and increase
> their efforts toward getting the schools finished. She/He is correct that, if
> this is the case, the null result should not be surprising. However, looking
> into changes in outcomes in the control and the treatment we see no effect of
> proximity. Moreover, municipalities in Brazil are much insulated, and mayors
> usually belong to different parties. There are about 35 active parties in
> Brazil, which makes cross-municipality contact and information sharing costly
> and difficult. Therefore, we believe that this possibility is remote.

>>>>

\noindent 28 December 2019

@@

Lastly, we have rewritten some parts of the main text to highlight two points:
1) that our experiment hinges on participation only; 2) that the effect of
mobilisation and pressure on school construction outcomes require further
analyses. We believe the paper now reflects our results more accurately.

Below we discuss in more detail these and other changes we have made to the
manuscript in response to comments we had received. We thank the editor again
for the opportunity to revise the manuscript, and the reviewer for his/her
extremely helpful comments.

@@

> We have made several changes to the main paper and the online appendix to
address this important concern. First, we have added a new section to the
appendix in order to clarify how we designed and conducted the experiment.
We copy the text below:

@@

> To answer these questions, we have added Google Analytics data on _Tá de
Pé_'s download and usage. This provide exogenous and reliable data about our
experimental manipulation and the effectiveness of the treatment. The data
confirm that app usage was significant. We add the following paragraph to the
main text to show user engagement (page 8):

@@

> _Data from Google Analytics suggest that users did engage with the TDP app.
On average, each user launched 60 app sessions, which indicates their interest
in the application. In total, the app had 53,928 screen visualisations, with an
average of 2.42 screen visualisations per session._

@@

> We fully agree with the reviewer and have changed the main text accordingly.
We have rewritten several passages, from the abstract to the discussion, in
order to highlight that our mechanism is indeed based on information provision
and not mobilisation _per se_. For instance, the first paragraph in the
Discussion session has been rewritten as:

@@

Other changes are marked as boldface in the main text.

@@

The Results section (page 9) has been rewritten as:

@@

> Lastly, the reviewer questions us about the possibility of
> cross-municipality contamination. This would mean that the existence of the
> app in a municipality could make mayors in other municipalities to act and
> increase their efforts toward getting the schools finished. She/He is correct
> that, if this is the case, the null result should not be surprising. However,
> looking into changes in outcomes in the control and the treatment we see no
> effect of proximity. Moreover, municipalities in Brazil are much insulated,
> and mayors usually belong to different parties. There are about 35 active
> parties in Brazil, which makes cross-municipality contact and information
> sharing costly and difficult. Therefore, we believe that this possibility is
> remote.
